Relating games of Menger, countable fan tightness, and selective separability

### 2018-03-02 articles/relating-games-menger-cft-ss/article.tex
fix technical error by applying AC

\begin{lemma}\label{mengerFanLemma1}
  Let \(X\) be a \(T_{3\frac{1}{2}}\) topological space.
  If \(X\) is \(\Omega M\)
  (resp. \(\Omega M^+\), \(\Omega M^{\plusMark}\)).
  then \(C_p(X)\) is \(CFT_{\vec 0}\)
  (resp. \(CFT_{\vec 0}^+\), \(CFT_{\vec 0}^{\plusMark}\)).
\end{lemma}

@@

  Consider the sequence of blades
  \(\<B_0,B_1,\dots\>\in\Omega_{C_p(X),\vec 0}^\omega\), and the
  corresponding sequence of \(\omega\)-covers
  \(\<\mc U_0(B_0),\mc U_1(B_1),\dots\>\in \Omega_X^\omega\).

  Assuming \(X\) is \(\Omega M\), choose a witness
  \(\<\mc F_0,\mc F_1,\dots\>\) such that
  \(\mc F_n\in[\mc U_n(B_n)]^{<\omega}\) and
  \[
    \bigcup_{i\leq n<\omega} \mc F_n
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    F_n
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \mc F_n
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}F_n}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\). Since \(\bigcup_{i\leq n<\omega} \mc F_n\)
  is an \(\omega\)-cover, we may choose
  \(i\leq n<\omega\) and
  \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
  Therefore, \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in F_n\cap[\vec 0,G,\epsilon]\), and thus
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}F_n\).

  Assuming \(X\) is \(\Omega M^+\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(\<B_0,\dots,B_n\>)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\). Since
  \(\bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
  is an \(\omega\)-cover, we may choose
  \(i\leq n<\omega\) and \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]
  \in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
  Therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\),
  and thus every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)\).

  Assuming \(X\) is \(\Omega M^{\plusMark}\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(B_n,n)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\mc U_n(B_n),n)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(B_n,n)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\). Since
  \(\bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)\) is an \(\omega\)-cover,
  we may choose \(i\leq n<\omega\) and
  \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
  Therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and thus
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(B_n,n)\).
\end{proof}

>>>>

\begin{lemma}\label{mengerFanLemma1}
  If \(X\) is \(\Omega M\)
  (resp. \(\Omega M^+\), \(\Omega M^{\plusMark}\)),
  then \(C_p(X)\) is \(CFT_{\vec 0}\)
  (resp. \(CFT_{\vec 0}^+\), \(CFT_{\vec 0}^{\plusMark}\)).
\end{lemma}

@@

  Consider the sequence of blades
  \(\<B_0,B_1,\dots\>\in\Omega_{C_p(X),\vec 0}^\omega\), and the
  corresponding sequence of \(\omega\)-covers
  \(\<\mc U_0(B_0),\mc U_1(B_1),\dots\>\in \Omega_X^\omega\).
  For \(U\in\mc U_n(B_n)\), choose \(\vec x_U\in B_n\) such that
  \(
    U
      =
    \vec x_U^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
  \).

  Assuming \(X\) is \(\Omega M\), choose a witness
  \(\<\mc F_0,\mc F_1,\dots\>\) such that
  \(\mc F_n\in[\mc U_n(B_n)]^{<\omega}\) and
  \[
    \bigcup_{i\leq n<\omega} \mc F_n
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Let
  \[
    F_n
      =
    \left\{
      \vec x_U
    :
      U
        \in
      \mc F_n
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}F_n}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\). Since \(\bigcup_{i\leq n<\omega} \mc F_n\)
  is an \(\omega\)-cover, we may choose
  \(i\leq n<\omega\) and
  \(U\in\mc F_n\)
  such that
  \[
    G
      \subseteq
    U
      =
    \vec x_U^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
      \subseteq
    \vec x_U^{\leftarrow}[(-\epsilon,\epsilon)]
  .\]
  It follows that \(\vec x_U\in F_n\cap[\vec 0,G,\epsilon]\), and thus
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}F_n\).

  Assuming \(X\) is \(\Omega M^+\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Let
  \[
    \tau(\<B_0,\dots,B_n\>)
      =
    \left\{
      \vec x_U
    :
      U
        \in
      \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\). Since
  \(\bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
  is an \(\omega\)-cover, we may choose
  \(i\leq n<\omega\) and
  \(U\in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
  such that
  \[
    G
      \subseteq
    U
      =
    \vec x_U^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
      \subseteq
    \vec x_U^{\leftarrow}[(-\epsilon,\epsilon)]
  .\]
  It follows that
  \(\vec x_U\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\),
  and thus every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)\).

  Assuming \(X\) is \(\Omega M^{\plusMark}\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Let
  \[
    \tau(B_n,n)
      =
    \left\{
      \vec x_U
    :
      U
        \in
      \sigma(\mc U_n(B_n),n)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(B_n,n)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\). Since
  \(\bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)\) is an \(\omega\)-cover,
  we may choose \(i\leq n<\omega\) and
  \(U\in\sigma(\mc U_n(B_n),n)\)
  such that
  \[
    G
      \subseteq
    U
      =
    \vec x_U^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
      \subseteq
    \vec x_U^{\leftarrow}[(-\epsilon,\epsilon)]
  .\]
  It follows that \(\vec x_U\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and thus
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(B_n,n)\).
\end{proof}
